---
title: "W_UP_01"
author: "iboniarchie"
date: "summer2021"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The boxplot shows that skill players do more pushups than line players. In the skill players boxplot the 25th percentile is higher than the boxplot of the line players 75th percentile  



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
# Numerical results

```{r}
favstats(pushups~position,data=mydata)
```

numerical results show that the average number of pushups done by a line player is 17 and the average number of pushups done by a skill player if 50  



## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

# Inferential  
  
```{r}
t.test(pushups~position,data=mydata)
```

P-value is low. We have to reject the null hypothesis.There is a difference between the amount of pushups that a skill player does. Skill players on average can perform three times the amount that line players.    

# Discussion and conclusion 

Variable analysis was done examined variables given in order to help identitfy which helper file is needed. We used the Numerica~Cat file to help make since of this file. I copied and pasted the commands and changed the variables within the command. Conclusion from the results was to reject  the null hypotheseis. Meaning there was a major difference in the amount of pushups that the skill players performed than the line players.

